Adaptive Sequential Model Selection

### 2015-07-11 paper.tex
rob page 21

Note that  (\ref{eq:boot})  has the form of  (conditional) parametric bootstrap sampling, in which the bootstrap residuals projected into the subspace
orthogonal to the current fit.  The typical justification for the bootstrap is asymptotic, relying on the convergence of the parameter estimates to the true parameters.
But something magical  occurs in the selective sampling scheme (\ref{eq:boot}): this  sampling fixes the value of $ X_{E_{k-1}}^Ty$ and this conditioning
removes the dependence on nuisance parameters.
Hence  (\ref{eq:boot}) yields the exact (non-asymptotic) conditional distributions and p-values.

>>>>

Note that  (\ref{eq:boot})  has the form of  (conditional) parametric bootstrap sampling, but  with  a novel twist:  the bootstrap residuals are projected into the subspace
orthogonal to the current fit.  The typical justification for the bootstrap is asymptotic, relying on the convergence of the parameter estimates to the true parameters.
But something magical  occurs in the selective sampling scheme (\ref{eq:boot}): this  sampling fixes the value of $ X_{E_{k-1}}^Ty$ and this conditioning
removes the dependence on nuisance parameters.
Hence  (\ref{eq:boot}) yields the exact (non-asymptotic) conditional distributions and p-values.
